Supervised Learning for Psychological Attention to High School Students

### 2020-11-18 article/inputs/svm.tex
[ article ] Added RBF kernel explanation.

>>>>

The RBF kernel SVM had the second-best performance, as at least it was able to
recognize some of the data from class 1 (in comparison to the Linear SVM). This
is expected as in each of the projections the data did not present any circular
relationship. This issue with using an RBF kernel can be visualized in Fig.
\ref{fig:svm-rbf}.

It is important to note, that, as with all the SVMs, the contour plotted
preserves the structure of the used kernel and therefore confirms that the
procedure used is correct.
